Generate data for multispecies modeling, including diet!

### 2020-08-06 NOBAmsdiets.Rmd
need to load detailed diet, a bear

The true data can be generated without updated config files (once I fix missing diets in wrappers!):

```{r OMtruth}

@@

>>>>

The true data can be generated without updated config files (once I fix missing diets in wrappers!).

UPDATE: added an option to bring in biomass_eaten in the om_species wrapper. However, the way this is calculated is probably inappropriate for what we want. biomass_eaten is the output of box specific total tons consumed by predators from PROD.nc split by global diet comp from DietCheck.txt. This means predators will have the same diet comp in all boxes, whether prey were there or not.

To do diet sampling using our survey design, we need to retain actual box-specific diet. This is found in the DetailedDietCheck.txt file, which outputs tons consumed since last timestep for each predator by box, layer, and prey. Because there is no conversion needed for tons, we can just read this in, get rid of all the zero diet comp values to make it a (possibly) manageable size, and apply the survey from there. A new function `load_detailed_diet_comp.R` is developed below.

Bottom line is don't use biomass_eaten; maybe we should take it out of `run_truth()` output.

```{r OMtruth, eval=FALSE}

@@

cod5.365 <- NOBAom_ms$truebioeaten_ss %>%
  filter(species=="North_atl_cod",
         agecl==5,
         time.days==365, 
         polygon==4)

cod5.365.check <- ms_diet %>%
  filter(species=="North_atl_cod",
         agecl==5,
         time.days==365)

#it does, but I think we need this by box
#it makes no sense to apply global diet comp to boxes, not all prey 
#may be in the box
#DetailedDietCheck.txt is the file to read for using survey sampling.

#this file is huge, try data.table::fread
detaileddiettest <- data.table::fread(file.path(here("atlantisoutput", "NOBAwithAnnAgeOutput"), "outputnordic_runresults_01DetailedDietCheck.txt"),
                                      data.table=FALSE
                                      #nrows = 200
                                      )

diet <- detaileddiettest

#remove rows that are all 0 prey
#diet <- diet[apply(diet[,-c(1:5)], 1, function(x) !all(x==0)),]

#should do the same thing faster
diet <- diet[as.logical(abs(as.matrix(diet[,-c(1:5)])) %*% rep(1L,ncol(diet[,-c(1:5)]))), ]

#test pieces of new load_detailed_diet function
  if(length(grep("Group",colnames(diet)))>0)
    colnames(diet) <- gsub("Group","Predator",colnames(diet))

  # Change column order
  diet <- diet[, c("Predator", "Cohort", "Time", "Box", "Layer",
    names(diet)[which(!names(diet) %in% c("Predator", "Cohort", "Time", "Box", "Layer"))])]

  # Convert to tidy dataframe to allow joining/merging with other dataframes.
  diet <- tidyr::gather_(data = diet, key_col = "prey", value_col = "dietcomp",
    #gather_cols = names(diet)[(which(names(diet) == "Updated") + 1):NCOL(diet)])
    gather_cols = names(diet)[(which(names(diet) %in% fgs$Code))])

  # Get rid of 0 dietcomp rows to make manageable size
  diet <- filter(diet, dietcomp>0)

  names(diet) <- tolower(names(diet))

  diet$prey <- as.character(diet$prey)
  diet$predator <- as.character(diet$predator)

  # Change species acronyms to actual names.
  species_names <- fgs[, c("Name", "Code")]
  diet$species <- species_names$Name[match(diet$predator, species_names$Code)]
  diet$prey <- species_names$Name[match(diet$prey, species_names$Code)]

  # diet outputs are not all divisible by toutinc, leave in days
  diet$time.days <- diet$time #/ toutinc

  #fix cohort to agecl

  diet <- diet %>%
    dplyr::mutate(agecl = cohort + 1)

  # drop redundant columns and reorder
  diet <- diet[,c("species", "agecl", "time.days", "box", "layer", "prey", "dietcomp")]
